\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sebastian Iglesias} \\ \vspace{1pt}
    \href{mailto:me@sebiglesias.com.ar}{\underline{me@sebiglesias.com.ar}} $|$ 
    \href{https://linkedin.com/in/sebiglesias}{\underline{linkedin.com/in/sebiglesias}} $|$
    \href{https://github.com/sebiglesias}{\underline{github.com/sebiglesias}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ITBA University}{Buenos Aires, Argentina}
      {Postgraduate Course, Data Science specialization}{Aug. 2019 -- Aug. 2020}
    \resumeSubheading
      {Austral University}{Buenos Aires, Argentina}
      {Master in Software Engineer}{Feb. 2014 -- Dec. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate Professor}{Febraury 2023 -- Present}
      {Universidad Austral}{Buenos Aires, Argentina}
      \resumeItemListStart
        \resumeItem{Preparing and giving classes and assignments to software engineer students.}
        \resumeItem{Introduction to Programming 1 (1st-year students): Basic Python and programming principles, use of a standard POSIX terminal, git, and GitHub}
        \resumeItem{Laboratory I (3rd-year students):
        This course provides the fundamental knowledge required to develop a software project, covering all stages from conception to implementation and testing. Students work in groups and propose real-life software projects, using use case analysis to define requirements and create an implementation schedule. The course evaluates progress through two partial deliveries, where each group showcases their use case implementations using the developed software.}
        \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{July 2022 -- Present}
      {Caribou}{Remote role}
      \resumeItemListStart
        \resumeItem{At Caribou, we are building healthcare cost prediction and optimization software for the finance industry. Financial advisors and wealth managers across the US are using our software for proactive healthcare planning, protecting their client’s wealth, and building stronger client relationships. Every feature we release or conversation we have fits our mission of creating a world where healthcare does not get in the way of living.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Senior Software Engineer}{December 2017 -- July 2022}
      {MuleSoft, a Salesforce company}{Buenos Aires, Argentina}
      \resumeItemListStart
        \resumeItem{Senior Software Engineer: Developed Mulesoft RPA, adapting a legacy codebase to Mulesoft's coding style. Used Java and Spring microservices that interacted with a Postgresql database with migrations managed by Liquibase interacting with different engineering departments. (Jul 2021 -- Jul 2022)}
        \resumeItem{Software Engineer: Developed Anypoint's Datagraph in an engineering team following agile methodologies, developing frontend and backend services. In conjunction with my team, we developed REST Services using Java and Spring as well as web clients with React, Redux, and Typescript. Developed integration tests using Testcafe. (Feb 2020 -- Jul 2021}
        \resumeItem{Associate Software Engineer: Developed Monitoring Platform inside Mulesoft's Anypoint Platform in an engineering team following agile methodologies, developing front and backend services. In conjunction with my team, we developed REST Services using Scala, Akka, and Java and several types of databases as well as web clients with React, Angular, and Typescript. Which were deployed in the AWS cloud via tools such as Terraform, salt, spinnaker and Jenkins. For Monitoring purposes, I've worked with the elastic search stack and set up scripts on Python and bash.}
    \resumeItemListEnd

    \resumeSubheading
      {Information Technology Teacher}{April 2016 -- December 2016}
      {FINES}{Buenos Aires, Argentina}
      \resumeItemListStart
        \resumeItem{Worked as a teacher in IT for an accelerated high school course for adults under the FINES plan. I planned and gave night classes to both adults and teenagers.}
      \resumeItemListEnd

    \resumeSubheading
      {Volunteer}{March 2015 -- May 2015}
      {Entrepreneur 4 Entrepreneur}{Buenos Aires, Argentina}
      \resumeItemListStart
        \resumeItem{Volunteer in consulting and IT area. Studied and applied LEAN startup methodologies to assist other entrepreneurs and also did some web development for the consulting company.}
      \resumeItemListEnd
    
    \resumeSubheading
      {IT Manager}{August 2014 -- February 2015}
      {I-Gen Latam}{Buenos Aires, Argentina}
      \resumeItemListStart
        \resumeItem{Computer repairing, MySQL database management, PHP and web development and maintained a legacy report generation system.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Informatica Solidaria} $|$ \emph{NGO organization}}{September 2015 -- September 2017}
          \resumeItemListStart
            \resumeItem{Founded Informatica Solidaria, an organization that received old electronics, repaired and donated them to educational organizations in Pilar, Buenos Aires, Argentina.}
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
      %     \resumeItemListStart
      %       \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
      %       \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
      %       \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
      %       \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, Scala, SQL (Postgres and MySQL), Typescript, JavaScript, HTML/CSS, R, Bash, Terraform, SaltStack, Angular} \\
     \textbf{Frameworks and Libraries}{: React, Node.js, Express.js, JUnit, Playwright, Material-UI, FastAPI, GraphQL, Redux, Pandas, NumPy, Storybook, TestCafe} \\
     \textbf{Developer Tools}{: Git, Docker, Jenkins, Spinnaker, CircleCI, Google Cloud Platform (GCP), Amazon Web Services (AWS), IntelliJ, Liquibase, Postman, Linux, Slack} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
